MSc Thesis

### 2023-05-29 manuscript/main.tex
added the pedigree table

\listfiles
\documentclass[12pt, letterpaper, ]{report}
\usepackage[style=authoryear, maxnames=2, maxbibnames=99, citestyle=apa]{biblatex}
\addbibresource{merged_biblio2.bib}
\addbibresource{internet_stuff.bib}
%\addbibresource{induction.bib}
%\addbibresource{gwas_silicon.bib}
\usepackage{caption}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{url}
\usepackage{lineno}
\usepackage{tabularx}
\usepackage{gensymb}
\usepackage{longtable}
\usepackage{titlesec}
\usepackage{subcaption}
\newcommand{\mycomment}[1]{}
% Change chapter heading font size to 14pt
\titleformat{\chapter}{\Large\bfseries}{\thechapter.}{20pt}{\Large}

@@

\begin{figure}[h]
        \includegraphics[width = \textwidth]{images/phenolic_silicon_regression.png}
        \centering
        \caption{Scatter plot of the relationship between leaf silicon and leaf phenolic concentration}
        \label{Fig:phe_si_scatter}
\end{figure}

@@

\begin{figure}[h]
        \centering
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/tf_si_plot.png}
                \label{Fig:tf_si_peak}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/sc_si_plot.png}
                \label{Fig:sc_si_peak}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/gh_si_plot.png}
                \label{Fig:gh_si_peak}
        \end{subfigure}
        \caption{Manhattan plots of the results of our GWAS analysis for leaf silicon content in \textit{Aegilops tauschii}. Red dots indicate a negative correlation, while blue dots denote a positive correlation. The top two plots show the results for the outdoor growing environments, and the bottom plot is the glasshouse environment.}
        \label{Fig:si_peak_plot}
\end{figure}

\begin{figure}[h]
        \centering
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/tf_mn_plot.png}
                \label{Fig:tf_mn_peak}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/sc_mn_plot.png}
                \label{Fig:sc_mn_peak}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/gh_mn_plot.png}
                \label{Fig:gh_mn_peak}
        \end{subfigure}
        \caption{Manhattan plots of the results of our GWAS analysis for leaf manganese content in \textit{Aegilops tauschii}. Red dots indicate a negative correlation, while blue dots denote a positive correlation. The top two plots show the results for the outdoor growing environments, and the bottom plot is the glasshouse environment.}
        \label{Fig:mn_peak_plot}
\end{figure}

>>>>

\listfiles
\documentclass[12pt, letterpaper, ]{report}
\usepackage[style=authoryear, maxnames=2, maxbibnames=99, citestyle=apa]{biblatex}
\addbibresource{merged_biblio2.bib}
\addbibresource{internet_stuff.bib}
%\addbibresource{induction.bib}
%\addbibresource{gwas_silicon.bib}
\usepackage{caption}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{url}
\usepackage{lineno}
\usepackage{tabularx}
\usepackage{gensymb}
\usepackage{longtable}
\usepackage{titlesec}
\usepackage{subcaption}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{array}
\newcommand{\mycomment}[1]{}
% Change chapter heading font size to 14pt
\titleformat{\chapter}{\Large\bfseries}{\thechapter.}{20pt}{\Large}

@@

\begin{figure}[h]
        \includegraphics[width = \textwidth]{images/phenolic_silicon_regression.png}
        \centering
        \caption{Scatter plot of the relationship between leaf silicon and leaf phenolic concentration}
        \label{Fig:phe_si_scatter}
\end{figure}
\clearpage

\section{Supplementary Info}
\begin{landscape}
\begin{table}
        \centering
        \caption{Pedigrees of the cultivars used in this study}
        \begin{tabular}{ll>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{5cm}>{\raggedright\arraybackslash}p{4cm}}
          \toprule
          Species & Cultivar & Parent 1 & Parent 2 & Parent 1 Pedigree & Parent 2 Pedigree \\
          \midrule
          Barley & CDC Austenson & TR358 & 94Ab12271 & Not Available & Not Available \\
          Barley & AAC Synergy & TR02267 & Newdale & TR253/AC Metcalfe & CDC Stratus//TR236/WM862-6 \\
          Barley & CDC Copeland & WM861-5 & TR118 & Harrington & \\
          Oats & AC Morgan & OT526 & OT763 & 17578/Alfred & Fidler/Cascade \\
          Oats & Camden & SW Betania & Dominik & SW 151-7-95/SW 52-95 & Not Available \\
          Oats & AC Summit & Ronald & OT299 & W89329/AC Medallion & AC Rebel/Dumont 48 \\
          Triticale & Bunker & 95P105 & 85L0120006 & Pika-5/Yogui-1 & Spring triticale*n/RL4137 \\
          Triticale & Tyndal & Nimir-1/Hare-265//Erizo-9 & 88L012 & Nimir-1/Hare-265//Erizo-9 & Pronghorn*n/RL4137 \\
          Triticale & AB Stampeder & BULL 10/MANATI1//FARA S/CMH84.4414 & POLLMER 2.2.1 $\ast$2//FARA S/CMH84.4414 & BULL 10/MANATI1//FARA S/CMH84.4414 & POLLMER 2.2.1 $\ast$2//FARA S/CMH84.4414 \\
          Wheat & AAC Brandon & Superb/CDC Osler & ND744 & Superb/CDC Osler & ND2831/Parshall//ND706 \\
          Wheat & CDC Landmark & Unity & BW864 & McKenzie$\ast$3// BW174$\ast$2/Clark & YAQUI 50-ENANO/3$\ast$KALYANSONA \\
          Wheat & CDC Superb & BW282 & CDC Go & Not Available & Grandin/SD3055 \\
          \bottomrule
        \end{tabular}
      \end{table}

      \end{landscape}

@@

\begin{figure}[h]
        \centering
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/tf_si_plot.png}
                \label{Fig:tf_si_peak}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/sc_si_plot.png}
                \label{Fig:sc_si_peak}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/gh_si_plot.png}
                \label{Fig:gh_si_peak}
        \end{subfigure}
        \caption{Manhattan plots of the results of our GWAS analysis for leaf silicon content in \textit{Aegilops tauschii}. Red dots indicate a negative correlation, while blue dots denote a positive correlation. The top two plots show the results for the outdoor growing environments, and the bottom plot is the glasshouse environment. The dotted line represents the bonferroni-corrected significance threshold.}
        \label{Fig:si_peak_plot}
\end{figure}

\begin{figure}[h]
        \centering
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/tf_mn_plot.png}
                \label{Fig:tf_mn_peak}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/sc_mn_plot.png}
                \label{Fig:sc_mn_peak}
        \end{subfigure}
        \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[scale=0.3]{images/gwas_plots/svgtopng/gh_mn_plot.png}
                \label{Fig:gh_mn_peak}
        \end{subfigure}
        \caption{Manhattan plots of the results of our GWAS analysis for leaf manganese content in \textit{Aegilops tauschii}. Red dots indicate a negative correlation, while blue dots denote a positive correlation. The top two plots show the results for the outdoor growing environments, and the bottom plot is the glasshouse environment. The dotted line represents the bonferroni-corrected significance threshold.}
        \label{Fig:mn_peak_plot}
\end{figure}
